### 2019-02-26 README.Rmd
update readme

(Note that this preprint is currently very outdated, see below for more recent results)

@@

* [Manuscript](manuscript): Source files for producing the manuscript.
* [Package](package): An R package with several helper functions.
* [Raw](raw): Files generated by hand, such as figures and spreadsheets.
* [Derived](derived): Intermediate data files produced by the scripts. These files or not git committed.

@@

[Docker](https://docs.docker.com/install) has to be installed to run TI methods. See https://docs.docker.com/install for instructions. For windows 10 you can install [Docker CE](https://store.docker.com/editions/community/docker-ce-desktop-windows), older windows installations require the [Docker toolbox](https://docs.docker.com/toolbox/overview/).

@@

```{r, message = FALSE, echo = TRUE}
dynwrap::test_docker_installation(detailed = TRUE)
```

>>>>

*Note that this preprint is currently **very** outdated. An updated manuscript will be published soon, you can browse below for more recent results*

@@

* [Manuscript](manuscript): Source files for producing the manuscript.
* [Package](package): An R package with several helper functions for organizing the benchmark and rendering the manuscript.
* [Raw](raw): Files generated by hand, such as figures and spreadsheets.
* [Derived](derived): Intermediate data files produced by the scripts. These files are not git committed.

@@

[Docker](https://docs.docker.com/install) has to be installed to run TI methods. See https://docs.docker.com/install for instructions. For windows 10 you can install [Docker CE](https://store.docker.com/editions/community/docker-ce-desktop-windows), older Windows installations require the [Docker toolbox](https://docs.docker.com/toolbox/overview/).

@@

```{r, message = TRUE, echo = TRUE}
dynwrap::test_docker_installation(detailed = TRUE)
```
